---
title: "Archaeological Analysis"
output: html_notebook
---

```{r}
library("cowplot")
library("data.table")
library("dplyr")
library("ggplot2")
library("ggrepel")
library("FactoMineR")
library("factoextra")
library("plyr")
library("reshape2")
library("tidyr")
library("viridis")

# library(devtools)
# install_github('ISAAKiel/quantAAR')
library(quantAAR)

source("r/fcn.r")
```

see:
- [ ] http://www.sthda.com/english/rpkgs/factoextra/
- [ ] http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/113-ca-correspondence-analysis-in-r-essentials/#export-plots-to-pdfpng-files
- [ ] https://stackoverflow.com/questions/30891559/r-biplot-with-clusters-as-colors


## data preparation

### load & clean dataset 
```{r}
d <- read.csv("data/base/StyleAttributes.csv", encoding = 'UTF-8')
```

### replace vessel shape typology from Wotzka 1995 with universal typology for diachronic question:
```{r}
k <- read.csv("data/base/Wotzka1995_GefFormenKonkordanz.csv")
k$TypOrig <- paste("GefTyp.", k$TypHPW, sep = "")
k$TypNew <- paste("GefTyp.", k$TypDS, sep = "")

d$ATTR <- mapvalues(d$ATTR, 
          from = k$TypOrig, 
          to = k$TypNew)
```

### filter out rims as there is no universal typolgy jet
```{r}
d <- filter(d, !grepl("Rand", ATTR))

# filter out fabrics as no thorough analysis has been performed jet
#d <- filter(d, !grepl("Fabric", ATTR))
```

# Analysis of all styles and attributes

```{r}
plt <- anlys(d, 2)
plt$basicPlot
ggsave("img/1_all.png", width = 20, height = 10)
```

```{r}
plt$caPlot
ggsave("img/_all_ca.png", width = 20, height = 10)
```

```{r}
plt$ggplot
ggsave("img/_all_ggplot.png", width = 20, height = 10)
```

# Iterative filtering based on the initial CA

## Styles from cluster 1 & 2

```{r}
filt1.1 <- as.data.frame(subset(plt$hclust$cluster, plt$hclust$cluster == 1))
filt1.1 <- row.names(filt1.1)
filt1.1
```

```{r}
d1.1 <- subset(d, STYLE %in% filt1.1)
```


```{r}
filt1.2 <- as.data.frame(subset(plt$hclust$cluster, plt$hclust$cluster == 2))
filt1.2 <- row.names(filt1.2)
filt1.2
```

```{r}
d1.2 <- subset(d, STYLE %in% filt1.2)
```

### Cluster 1

```{r}
plt <- anlys(d1.1, 2)
plt$basicPlot
ggsave("img/1-1_all.png", width = 20, height = 10)
```

```{r}
plt$ggplot
ggsave("img/1-1_all_ggplot.png", width = 20, height = 10)
```

### Cluster 2

```{r}
plt <- anlys(d1.2, 2)
plt$basicPlot
ggsave("img/1-2_all.png", width = 20, height = 10)
```

```{r}
plt$ggplot
ggsave("img/1-2_all_ggplot.png", width = 20, height = 10)
```

## lock at Cluster 1 from #2

```{r}
filt2.1 <- as.data.frame(subset(plt$hclust$cluster, plt$hclust$cluster == 1))
filt2.1 <- row.names(filt2.1)
filt2.1
```

```{r}
d2.1 <- subset(d, STYLE %in% filt2.1)
```

```{r}
plt <- anlys(d2.1, 2)
plt$basicPlot
ggsave("img/2-1_all.png", width = 20, height = 10)
```

```{r}
plt$ggplot
ggsave("img/2-1_all_ggplot.png", width = 20, height = 10)
```

## lock at Cluster 2 from #3

```{r}
filt3.2 <- as.data.frame(subset(plt$hclust$cluster, plt$hclust$cluster == 2))
filt3.2 <- row.names(filt3.2)
filt3.2
```

```{r}
d3.2 <- subset(d, STYLE %in% filt3.2)
```

```{r}
plt <- anlys(d3.2, 2)
plt$basicPlot
ggsave("img/3-2_all.png", width = 20, height = 10)
```

```{r}
plt$ggplot
ggsave("img/3-2_all_ggplot.png", width = 20, height = 10)
```

## Styles from clusters 1 & 2

```{r}
filt4.1 <- as.data.frame(subset(plt$hclust$cluster, plt$hclust$cluster == 1))
filt4.1 <- row.names(filt4.1)
filt4.1
```

```{r}
d4.1 <- subset(d, STYLE %in% filt4.1)
```

```{r}
filt4.2 <- as.data.frame(subset(plt$hclust$cluster, plt$hclust$cluster == 2))
filt4.2 <- row.names(filt4.2)
filt4.2
```

```{r}
d4.2 <- subset(d, STYLE %in% filt4.2)
```

```{r}
plt <- anlys(d4.1, 2)
plt$basicPlot
ggsave("img/4-1_all.png", width = 20, height = 10)
```

```{r}
plt$ggplot
ggsave("img/4-1_all_ggplot.png", width = 20, height = 10)
```

```{r}
plt <- anlys(d4.2, 2)
plt$basicPlot
ggsave("img/4-2_all.png", width = 20, height = 10)
```

```{r}
plt$ggplot
ggsave("img/4-2_all_ggplot.png", width = 20, height = 10)
```


# Radiocabron datings (featuring c14bazAAr & aDRAC)

```{r}
#if(!require('devtools')) install.packages('devtools')
#devtools::install_github("ISAAKiel/c14bazAAR")
library(c14bazAAR)

library(oxcAAR)
```

```{r}
c14 <- get_aDRAC()
c14
```

```{r}
# TODO
# - filter for dates with Pottery
# - use oxcAAR() for summed 14C curves for the individual styles



```




