---
title: "Archaeological Analysis"
output: html_notebook
---

```{r}
library("cowplot")
library("data.table")
library("dplyr")
library("FactoMineR")
library("factoextra")
library("plyr")
library("reshape2")

# library(devtools)
# install_github('ISAAKiel/quantAAR')
library(quantAAR)

source("r/fcn.r")
```

see:
- [ ] http://www.sthda.com/english/rpkgs/factoextra/
- [ ] http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/113-ca-correspondence-analysis-in-r-essentials/#export-plots-to-pdfpng-files

## data preparation

### load & clean dataset 
```{r}
d <- read.csv("data/base/StyleAttributes.csv", encoding = 'UTF-8')
```

### replace vessel shape typology from Wotzka 1995 with universal typology for diachronic question:
```{r}
k <- read.csv("data/base/Wotzka1995_GefFormenKonkordanz.csv")
k$TypOrig <- paste("GefTyp", k$TypHPW, sep = "")
k$TypNew <- paste("GefTyp", k$TypDS, sep = "")

d$ATTR <- mapvalues(d$ATTR, 
          from = k$TypOrig, 
          to = k$TypNew)
```

### filter out rims as there is no universal typolgy jet
```{r}
d <- filter(d, !grepl("Rand", ATTR))

# filter out fabrics as no thorough analysis has been performed jet
#d <- filter(d, !grepl("Fabric", ATTR))
```


>> filter out varieties of vessel shapes and only go with base shape (A-J)


>> use function for iteratative analysis ... removing attributes or observations that distract the CA & clustering

```{r}
plt <- anlys(d, 2)
plt
ggsave("img/Anlys.png", width = 20, height = 10)
```



# combiing clusters & ca:

```{r}
c <- read.csv("data/processed/crosstab.csv", row.names = 1)

c.ca <- CA(c, 
           graph = FALSE)

c.hcpc <- HCPC(c.ca, 
               graph = FALSE, 
               max = 3)

# Dendrogram
clust.plt <- fviz_dend(c.hcpc)
# Individuals facor map
ca.plt <- fviz_cluster(c.hcpc)

bottom_row <- plot_grid(clust.plt, 
                        NULL, 
                        align = 'h', 
                        labels = c("B", "C"))
plt <- plot_grid(ca.plt, 
                 bottom_row,
                 ncol = 1, 
                 labels = c("A", ""), 
                 rel_heights = c(2, 1))
ggsave("img/Anlys2.png", width = 10, height = 10)
```



# remove styles NKB & LSL and rerun analysis

- both styles are part of the *North-Tradition* and ...

```{r}
d <- subset(d, STYLE != "NKB" & 
               STYLE != "LSL")
plt <- anlys(d, 2)
plt
ggsave("img/Anlys1.png", width = 20, height = 10)
```
















